\documentclass[12pt]{article}
\usepackage[style = numeric]{biblatex}
\begin{document}
\begin{thebibliography}{99}

	\bibitem{Paolo} Brandimarte, Paolo. ``Stock Portfolio Optimization."  \emph{Numerical Methods in Finance and Economics: A MATLAB-based Introduction}. 2nd ed. Hoboken, N.J.: Wiley Interscience, 2006. 65 - 81, 571. Print.

	\bibitem{C} Corliss, George. ``Which Root Does the Bisection Algorithm Find?" \emph{SIAM Rev. SIAM Review} 19.2 (1977): 325-27. Print.
	
	\bibitem{L} Lummer, Scott. ``Taming Your Optimizer: A Guide Through the Pitfalls of Mean-Variance Optimization." \emph{Global Asset Allocation: Techniques for Optimizing Portfolio Management}. Ed. Jess Lederman. Illustrated ed. Vol. 29. New York: Wiley, 1994. Print.
	
	\bibitem{Robert} Michaud, Richard O., and Robert Michaud. ``Estimation Error and Portfolio Optimization: A Resampling Solution." \emph{Journal Of Investment Management} 6.1 (2008): 8-28. Print.
	
	\bibitem{Pat2} Pat. ``Alpha Alignment." \emph{Portfolio Probe}. 9 July 2012. Web. 13 Oct. 2015.
	
	\bibitem{Pat} Pat. ``The Top 7 Portfolio Optimization Problems."  \emph{Portfolio Probe}. 5 Jan. 2012. Web. 4 Dec. 2015.

	\bibitem{Jay} Walters, Jay. ``What Is the Black-Litterman Model." \emph{BlackLitterman.org}. 2013. Web. 20 Nov. 2015.

	\bibitem{Wayne} Wayne, Thorp. ``Mean Variance Optimization."  \emph{Computerized Investing}. Web. 10 Oct. 2015.
	
	\bibitem{Winston} Winston, Wayne L. ``Nonlinear Programming."  \emph{Operations Research: Applications and Algorithms}. 4th ed. Belmont, Calif.: Duxbury, 2003. Print.

	
\end{thebibliography}
\end{document}